                \item Developed expertise in identifying top-tier catnip blends based on aroma, taste, and paw feel.
                \item Responsible for 15\% increase in nap productivity among colleagues by sharing personal stash.
            }
        \item \experience
            {Chief Box Inspector}
            {Amazon Cat Division}
            {USA}
            {Jan 2023 - Jun 2024}
            {
                \item Ensured all delivered boxes were adequately occupied and processed for coziness.
                \item Coordinated with fellow inspectors during high-paw-volume holiday seasons.
            }
    }

    \ProjectList{
        \item \project
            {MeowBit}{Jun 2021}
            {
                \item Designed an innovative, paw-friendly device to alert humans when food bowl levels are unacceptable.
                \item Incorporated advanced sound effects, including dramatic ``feed me'' meows and sad paw taps for heightened urgency.
                \item Received customer satisfaction feedback from fellow felines in beta testing.
            }
    }

    \EducationList{
        \item \education
            {Meowrizona State University}
            {Bachelor of Yarn Engineering}
            {USA}
            {May 2024}
    }

    \SkillList{
        \item \skillitem
            {Cat-Tongues}
            {
                Meow,
                Purr,
                Chirp,
                Hiss,
                Tail-Signaling
            }
    }

    \AchievementList{
        \item Fastest Zoomies Champion (2021) – Achieved record-breaking speeds around the house.
        \item Longest Nap (2020) – Successfully napped for 16 hours without interruption.
    }
\end{document}
